\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-09 paper/main.tex
minor changes on organization

\sloppy Serveral important application domains (e.g., transportation,
medical diagnosis, software development) use AI to optimize some
element of their business process. Deep Learning libraries~(DLLs)
(e.g., \jax, \torch{}, and \tf{}) provide the building blocks for the
AI components of these applications.  Unfortunately, as any piece of
software, these libraries contain bugs. An impressive number of
techniques have been recently proposed to find bugs in these
libraries~\Fix{cite 10+ fuzzing papers here}, however we observe that
the evaluation of these techniques do \emph{not} use a reference set
of reproducible bugs to evaluate their effectiveness. The lack of
evaluation standards is an obstacle to evaluate progress in this
important field.

This paper presents \tname, a database of curated reproducible bugs to
enable credible evaluation of DLL testing techniques.  Our dataset
currently consists of \numbugs{} environments to reproduce bugs across
three popular DLL libraries, namely, \jax, \tf, and \torch.

\Fix{...}

\begin{enumerate}

\sloppy  
\item \textbf{Handling bugs from nighly builds require saving wheels.}
  Many of the reproducible bugs rely on nightly builds since they can
  not be reproduced with any release builds. These nightly builds have
  a limited amount of time when they are publicly available, and they
  are de-indexed and removed after that time. In order to ensure bugs
  that depend on these nightly builds can be reproduced after these
  builds disappear, we save the whl files of these builds.

\item \textbf{Handling bugs in specific GPU-CUDA versions require OS
  changes:} Many of the GPU-related bugs can only be repro
  duced with
  specific GPU builds and specific CUDA builds. Changing different
  virtual environments does not change the CUDA versions of the
  system. That is why we use Docker when a bug relies on a specific
  version of CUDA to be installed in the system.

\end{enumerate}

Table~\ref{...}

\begin{table}
  \centering
  \caption{Characterization of reproducible bugs from \tname.}
\begin{tabular}{lrrr}
  \toprule
  & \multirow{2}{*}{\#} &  \multicolumn{1}{c}{build}          &   \multicolumn{1}{c}{enviroment}  \\
  &   & release-nightly &  venv-docker  \\
  \cmidrule(lr){2-4}
  \jax{} & 44 & 43-1 &  43-1 \\
  \torch{} & 33 & 15-18 & 19-14 \\
  \tf{} & 25 & 24-1 & 25-0 \\
  \midrule
  \multicolumn{1}{c}{$\Sigma$} & \numbugs{} & 82-20 & 87-15 \\
  \bottomrule
\end{tabular}
\end{table}

\section{Methodology}
\subsection{DLL and Bug Selection}
\subsection{Reproducing Bugs}
\subsection{}

>>>>

\sloppy Serveral important application domains (e.g., transportation,
medicine, etc.) use AI to optimize some element of their business
process. Deep Learning libraries~(DLLs), such as \jax, \torch{}, and
\tf{}, provide the building blocks for the AI components of these
applications.  Unfortunately, as any piece of software, these
libraries contain bugs. An impressive number of techniques have been
recently proposed to find bugs in these libraries~\Fix{cite 10+
  fuzzing papers here}, however we observe that the evaluation of
these techniques do \emph{not} use a reference set of reproducible
bugs to evaluate their effectiveness. The lack of evaluation standards
is an obstacle to the fair comparison of techniques, hindering
research progress.

This paper presents \tname, a database of curated reproducible bugs to
enable credible evaluation of DLL testing techniques. \tname\ is
equiped with a command-line interface to enable researchers to analyze
and reproduce bug instances.

\section{Methodology}

\begin{table}
  \centering
  \label{table:bug-characterization}
  \caption{Characterization of reproducible bugs from \tname.}
\begin{tabular}{lrrr}
  \toprule
  & \multirow{2}{*}{\#} &  \multicolumn{1}{c}{build}          &   \multicolumn{1}{c}{enviroment}  \\
  &   & release-nightly &  venv-docker  \\
  \cmidrule(lr){2-4}
  \jax{} & 44 & 43-1 &  43-1 \\
  \torch{} & 33 & 15-18 & 19-14 \\
  \tf{} & 25 & 24-1 & 25-0 \\
  \midrule
  \multicolumn{1}{c}{$\Sigma$} & \numbugs{} & 82-20 & 87-15 \\
  \bottomrule
\end{tabular}
\end{table}

Our dataset currently consists of \numbugs{} instances of reproducible
bugs representing three popular DLL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of bug
instances based on releases of the library against those based on
nightly builds, and column ``environment'' shows the breakdown of bug
instances that use Python's virtual environment against those that run
on a Docker container.

\subsection{Selection of Libraries}

\Fix{Abid, explain the rationale for selecting jax, torch, and tf.}

\subsection{Selection of Bugs}

\Fix{Abid, explain the selection criterion for the bugs.}

\subsection{Challenges in Bug Reproduction}

\textbf{Handling bugs from nighly builds require saving wheels.}  Many
of the reproducible bugs rely on nightly builds since they can not be
reproduced with any release builds. These nightly builds have a
limited amount of time when they are publicly available, and they are
de-indexed and removed after that time. In order to ensure bugs that
depend on these nightly builds can be reproduced after these builds
disappear, we save the whl files of these builds.

\textbf{Handling bugs in specific GPU-CUDA versions require OS
  changes:} Many of the GPU-related bugs can only be repro duced with
specific GPU builds and specific CUDA builds. Changing different
virtual environments does not change the CUDA versions of the
system. That is why we use Docker when a bug relies on a specific
version of CUDA to be installed in the system.

\subsection{Method}

\Fix{Abid, explain the method we used to create a bug instance}
